Building Markov State Models for Periodically Driven Non-Equilibrium Systems

### 2014-11-06 writedown/period.noneq.msm/submit.jctc/paper.tex
add the source for submission

\documentclass[aps, pre, preprint,unsortedaddress,a4paper,onecolumn]{revtex4}
% \documentclass[aps, pre, reprint,unsortedaddress,a4paper,twocolumn]{revtex4}
% \documentclass[acs, jctcce, a4paper,preprint,unsortedaddress,onecolumn]{revtex4-1}
% \documentclass[aps,pre,twocolumn,unsortedaddress]{revtex4-1}
% \documentclass[aps,jcp,groupedaddress,twocolumn,unsortedaddress]{revtex4}

\usepackage[fleqn]{amsmath}
\usepackage{amssymb}
\usepackage[dvips]{graphicx}
\usepackage{color}
\usepackage{tabularx}
\usepackage{algorithm}
\usepackage{algorithmic}

@@

@@

\title{Building Markov State Models for Periodically Driven Non-Equilibrium Systems}
\author{Han Wang}
\email{han.wang@fu-berlin.de}
\affiliation{CAEP Software Center for High Performance Numerical Simulation, Beijing, China}
\affiliation{Zuse Institute Berlin, Germany}
\author{Christof Sch\"utte}
\email{Christof.Schuette@fu-berlin.de}
\affiliation{Institute for Mathematics, Freie Universit\"at Berlin, Germany}
\affiliation{Zuse Institute Berlin, Germany}

\begin{abstract}
Recent years have seen an increased interest in non-equilibrium molecular dynamics (NEMD) simulations, especially for molecular systems with periodic forcing by external fields, e.g., in the context of studying  effects of electromagnetic radiation on the human body tissue. Lately, an NEMD methods with local thermostating has been proposed that allows for studying 
non-equilibrium processes in a statistically reliable and thermodynamically consistent way. In this article, we demonstrate how to construct Markov State Models (MSMs) for such NEMD simulations. MSM building has been well-established for systems in equilibrium where MSMs with just a few (macro-)states allow for accurate reproduction of the essential kinetics of the molecular system under consideration. Non-equilibrium MSMs have been lacking so far. The article presents how to construct such MSMs and illustrates their validity and usefulness for the case of conformation dynamics of alanine dipeptide in an external electric field.  
\end{abstract}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.3\textwidth]{fig/confs/c-2.eps}
  \caption{A schematic plot of the alanine dipeptide molecule and the dihedral angles $\phi$ and $\psi$.}
  \label{fig:tmp1}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.45\textwidth]{fig/t010/discrete/fig-cg-prob.eps}  
  \caption{Time-dependent probability $\prob\big(\phi_t\in[0,180), \psi_t\in [0,180)\big)$.  The brute force NEMD simulation is compared with different
    spatial discretization methods. The red shadow region indicates the
    statistical uncertainty of the NEMD simulation.}
  \label{fig:tmp2}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.45\textwidth]{fig/t010/discrete/fig-cg-prob-tau.eps}  
  \caption{Time-dependent probability $\prob\big(\phi\in[0,180), \psi\in [0,180)\big)$.  The NEMD simulation is compared with the Master equation using generators discretized with $N_\dih=20$ and different lag time $\tau$. The red shadow region indicates the
    statistical uncertainty of the NEMD simulation.}
  \label{fig:tmp3}
\end{figure}

@@

\begin{figure}
  \centering  
  \includegraphics[width=0.4\textwidth]{fig/t010/cluster.marco.3.steadyDist//fig-dist.eps}\\
  % \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-dist-msm.eps}
  \includegraphics[width=0.4\textwidth]{fig/t010/cluster.marco.3/fig-floquet-vec-1.eps}
  \caption{The color-scale plot of the logarithmic quasi-stationary distribution $\mymu$
    of (a) the NEMD  and (b)
    the discretized dynamics governed by Floquet transition matrix $\vect P=\myphi^{\top}(T)$.
  }
  \label{fig:num-1}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.4\textwidth]{fig/t010/cluster.marco.3/fig-cluster.eps}
  \caption{The core set identification. Different colors indicate different core sets: $C_{\confaa}$ (green), $C_\beta$ (yellow) and $C_{\confc}$ (red).
    The blue color indicates the transition region $C$ that does not belong to one of the core sets.}
  \label{fig:cluster}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3.fht/fig-fht-1.eps}
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3.fht/fig-fht-msm-1.eps}\\
  \vskip -.7cm
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3.fht/fig-fht-2.eps}
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3.fht/fig-fht-msm-2.eps}\\
  \vskip -.7cm
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3.fht/fig-fht-3.eps}
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3.fht/fig-fht-msm-3.eps}\\
  \vskip -.5cm
  \caption{Comparisons of the first mean hitting time (FMHT) based on NEMD
    simulation (left column) and discretized dynamics (right column).  From top
    to bottom the first mean hitting times to the core sets $C_{\confaa}$, $C_{\beta}$,
    and $C_{\confc}$ are shown, respectively}
  \label{fig:num-6}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Forward and backward committors}
\label{sec:alanine-committor}
\begin{figure}
  \centering
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-fw-1.eps}
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-fw-msm-1.eps}\\
  \vskip -.7cm
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-bw-1.eps}
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-bw-msm-1.eps}\\
  \vskip -.7cm
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-diff-1.eps}
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-diff-msm-1.eps}
  \vskip -.5cm
  \caption{Forward $q^\fwd_{\confaa}$ and backward 
    $q^\bwd_{\confaa}$ committors
    and their difference $q^\fwd_{\confaa} - q^\bwd_{\confaa}$
    computed from the NEMD trajectories (left
    column) and the  discretized dynamics (right column).}
  \label{fig:num-3}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-fw-2.eps}
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-fw-msm-2.eps}\\
  \vskip -.7cm
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-bw-2.eps}
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-bw-msm-2.eps}\\
  \vskip -.7cm
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-diff-2.eps}
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-diff-msm-2.eps}\\
  \vskip -.5cm
  \caption{Forward $q^\fwd_{\beta}$ and backward
    $q^\bwd_{\beta}$ committors
    and their difference  $q^\fwd_{\beta} - q^\bwd_{\beta}$ 
    computed from NEMD trajectories (left
    column) and the  discretized dynamics (right column).}
  \label{fig:num-4}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-fw-3.eps}
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-fw-msm-3.eps}\\
  \vskip -.7cm
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-bw-3.eps}
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-bw-msm-3.eps}\\
  \vskip -.7cm
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-diff-3.eps}
  \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-commitor-diff-msm-3.eps}\\
  \vskip -.5cm
  \caption{Forward $q^\fwd_{\confc}$ and backward $q^\bwd_{\confc}$
    committors
    and their difference  $q^\fwd_{\confc} - q^\bwd_{\confc}$ 
    computed from NEMD trajectories (left
    column) and the  discretized dynamics (right column).}
  \label{fig:num-5}
\end{figure}

@@

% \begin{figure}
%   \centering
%   \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-eig-vec-2.eps}
%   \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-eig-vec-3.eps}
%   \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-eig-vec-4.eps}\\
%   \caption{The eigenfunctions of $P$.}
%   \label{fig:num-6}
% \end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.4\textwidth]{fig/t010/cluster.marco.3/fig-coreset-prob.eps}
  \caption{Comparison of NEMD and MSM long-term kinetics of alanine
    dipeptide in an oscillatory electric field. The plots show the
    time-dependent probability $\hat p_j(t)$ to be assigned to
    core set $C_j$ (corresponding to the observable $\mathcal A$ given
    in (\ref{A}) with $\alpha_j=1$ and $\alpha_k=0$ for $k\not=
    j$). Solid lines are from brute force NEMD simulations, while the
    dashed lines are from our MSM.}
  \label{fig:num-7}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.48\textwidth]{fig/flowchart/flowchart2.eps}
  \caption{Flowchart showing optional procedures for MSM building based on NEMD trajectories. A lighter color indicates
  a "coarser'' approximation to the original NEMD dynamics. Please note that "equivalence" only means that the respective procedures result in the same matrix/MSM if one assumes perfect sampling.}
  \label{fig:flowchart}
\end{figure}

@@

\bibliography{ref}{}
\bibliographystyle{unsrt}

>>>>

\documentclass[journal=jctcce,manuscript=article]{achemso}
% \documentclass[aps, pre, preprint,unsortedaddress,a4paper,onecolumn,showkeys]{revtex4}
% \documentclass[aps, pre, reprint,unsortedaddress,a4paper,twocolumn]{revtex4}
% \documentclass[acs, jctcce, a4paper,preprint,unsortedaddress,onecolumn]{revtex4-1}
% \documentclass[aps,pre,twocolumn,unsortedaddress]{revtex4-1}
% \documentclass[aps,jcp,groupedaddress,twocolumn,unsortedaddress]{revtex4}
\usepackage[version=3]{mhchem} % Formula subscripts using \ce{}
\setkeys{acs}{keywords = true}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
% \usepackage{color}
% \usepackage{tabularx}
% \usepackage{algorithm}
% \usepackage{algorithmic}

@@

\title{Building Markov State Models for Periodically Driven Non-Equilibrium Systems}
\author{Han Wang}
\email{han.wang@fu-berlin.de}
\affiliation{CAEP Software Center for High Performance Numerical Simulation, Beijing, China}
\alsoaffiliation{Zuse Institute Berlin, Germany}
\author{Christof Sch\"utte}
\email{Christof.Schuette@fu-berlin.de}
\affiliation{Institute for Mathematics, Freie Universit\"at Berlin, Germany}
\alsoaffiliation{Zuse Institute Berlin, Germany}

@@

\begin{abstract}
Recent years have seen an increased interest in non-equilibrium molecular dynamics (NEMD) simulations, especially for molecular systems with periodic forcing by external fields, e.g., in the context of studying  effects of electromagnetic radiation on the human body tissue. Lately, an NEMD methods with local thermostating has been proposed that allows for studying 
non-equilibrium processes in a statistically reliable and thermodynamically consistent way. In this article, we demonstrate how to construct Markov State Models (MSMs) for such NEMD simulations. MSM building has been well-established for systems in equilibrium where MSMs with just a few (macro-)states allow for accurate reproduction of the essential kinetics of the molecular system under consideration. Non-equilibrium MSMs have been lacking so far. The article presents how to construct such MSMs and illustrates their validity and usefulness for the case of conformation dynamics of alanine dipeptide in an external electric field.  \\
\textbf{Keywords:} {Non-equilibrium, Markov states model, Alanine dipeptide, Electric field, Floquet theory}
\end{abstract}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.3\textwidth]{c-2.eps}
  \caption{A schematic plot of the alanine dipeptide molecule and the dihedral angles $\phi$ and $\psi$.}
  \label{fig:tmp1}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.45\textwidth]{fig-cg-prob.eps}  
  \caption{Time-dependent probability $\prob\big(\phi_t\in[0,180), \psi_t\in [0,180)\big)$.  The brute force NEMD simulation is compared with different
    spatial discretization methods. The red shadow region indicates the
    statistical uncertainty of the NEMD simulation.}
  \label{fig:tmp2}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.45\textwidth]{fig-cg-prob-tau.eps}  
  \caption{Time-dependent probability $\prob\big(\phi\in[0,180), \psi\in [0,180)\big)$.  The NEMD simulation is compared with the Master equation using generators discretized with $N_\dih=20$ and different lag time $\tau$. The red shadow region indicates the
    statistical uncertainty of the NEMD simulation.}
  \label{fig:tmp3}
\end{figure}

@@

\begin{figure}
  \centering  
  \includegraphics[width=0.4\textwidth]{fig-dist.eps}\\
  % \includegraphics[width=0.23\textwidth]{fig/t010/cluster.marco.3/fig-dist-msm.eps}
  \includegraphics[width=0.4\textwidth]{fig-floquet-vec-1.eps}
  \caption{The color-scale plot of the logarithmic quasi-stationary distribution $\mymu$
    of (a) the NEMD  and (b)
    the discretized dynamics governed by Floquet transition matrix $\vect P=\myphi^{\top}(T)$.
  }
  \label{fig:num-1}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.4\textwidth]{fig-cluster.eps}
  \caption{The core set identification. Different colors indicate different core sets: $C_{\confaa}$ (green), $C_\beta$ (yellow) and $C_{\confc}$ (red).
    The blue color indicates the transition region $C$ that does not belong to one of the core sets.}
  \label{fig:cluster}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.23\textwidth]{fig-fht-1.eps}
  \includegraphics[width=0.23\textwidth]{fig-fht-msm-1.eps}\\
  \vskip -.7cm
  \includegraphics[width=0.23\textwidth]{fig-fht-2.eps}
  \includegraphics[width=0.23\textwidth]{fig-fht-msm-2.eps}\\
  \vskip -.7cm
  \includegraphics[width=0.23\textwidth]{fig-fht-3.eps}
  \includegraphics[width=0.23\textwidth]{fig-fht-msm-3.eps}\\
  \vskip -.5cm
  \caption{Comparisons of the first mean hitting time (FMHT) based on NEMD
    simulation (left column) and discretized dynamics (right column).  From top
    to bottom the first mean hitting times to the core sets $C_{\confaa}$, $C_{\beta}$,
    and $C_{\confc}$ are shown, respectively}
  \label{fig:num-6}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Forward and backward committors}
\label{sec:alanine-committor}
\begin{figure}
  \centering
  \includegraphics[width=0.23\textwidth]{fig-commitor-fw-1.eps}
  \includegraphics[width=0.23\textwidth]{fig-commitor-fw-msm-1.eps}\\
  \vskip -.7cm
  \includegraphics[width=0.23\textwidth]{fig-commitor-bw-1.eps}
  \includegraphics[width=0.23\textwidth]{fig-commitor-bw-msm-1.eps}\\
  \vskip -.7cm
  \includegraphics[width=0.23\textwidth]{fig-commitor-diff-1.eps}
  \includegraphics[width=0.23\textwidth]{fig-commitor-diff-msm-1.eps}
  \vskip -.5cm
  \caption{Forward $q^\fwd_{\confaa}$ and backward 
    $q^\bwd_{\confaa}$ committors
    and their difference $q^\fwd_{\confaa} - q^\bwd_{\confaa}$
    computed from the NEMD trajectories (left
    column) and the  discretized dynamics (right column).}
  \label{fig:num-3}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.23\textwidth]{fig-commitor-fw-2.eps}
  \includegraphics[width=0.23\textwidth]{fig-commitor-fw-msm-2.eps}\\
  \vskip -.7cm
  \includegraphics[width=0.23\textwidth]{fig-commitor-bw-2.eps}
  \includegraphics[width=0.23\textwidth]{fig-commitor-bw-msm-2.eps}\\
  \vskip -.7cm
  \includegraphics[width=0.23\textwidth]{fig-commitor-diff-2.eps}
  \includegraphics[width=0.23\textwidth]{fig-commitor-diff-msm-2.eps}\\
  \vskip -.5cm
  \caption{Forward $q^\fwd_{\beta}$ and backward
    $q^\bwd_{\beta}$ committors
    and their difference  $q^\fwd_{\beta} - q^\bwd_{\beta}$ 
    computed from NEMD trajectories (left
    column) and the  discretized dynamics (right column).}
  \label{fig:num-4}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.23\textwidth]{fig-commitor-fw-3.eps}
  \includegraphics[width=0.23\textwidth]{fig-commitor-fw-msm-3.eps}\\
  \vskip -.7cm
  \includegraphics[width=0.23\textwidth]{fig-commitor-bw-3.eps}
  \includegraphics[width=0.23\textwidth]{fig-commitor-bw-msm-3.eps}\\
  \vskip -.7cm
  \includegraphics[width=0.23\textwidth]{fig-commitor-diff-3.eps}
  \includegraphics[width=0.23\textwidth]{fig-commitor-diff-msm-3.eps}\\
  \vskip -.5cm
  \caption{Forward $q^\fwd_{\confc}$ and backward $q^\bwd_{\confc}$
    committors
    and their difference  $q^\fwd_{\confc} - q^\bwd_{\confc}$ 
    computed from NEMD trajectories (left
    column) and the  discretized dynamics (right column).}
  \label{fig:num-5}
\end{figure}

@@

% \begin{figure}
%   \centering
%   \includegraphics[width=0.23\textwidth]{fig-eig-vec-2.eps}
%   \includegraphics[width=0.23\textwidth]{fig-eig-vec-3.eps}
%   \includegraphics[width=0.23\textwidth]{fig-eig-vec-4.eps}\\
%   \caption{The eigenfunctions of $P$.}
%   \label{fig:num-6}
% \end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.4\textwidth]{fig-coreset-prob.eps}
  \caption{Comparison of NEMD and MSM long-term kinetics of alanine
    dipeptide in an oscillatory electric field. The plots show the
    time-dependent probability $\hat p_j(t)$ to be assigned to
    core set $C_j$ (corresponding to the observable $\mathcal A$ given
    in (\ref{A}) with $\alpha_j=1$ and $\alpha_k=0$ for $k\not=
    j$). Solid lines are from brute force NEMD simulations, while the
    dashed lines are from our MSM.}
  \label{fig:num-7}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.48\textwidth]{flowchart2.eps}
  \caption{Flowchart showing optional procedures for MSM building based on NEMD trajectories. A lighter color indicates
  a "coarser'' approximation to the original NEMD dynamics. Please note that "equivalence" only means that the respective procedures result in the same matrix/MSM if one assumes perfect sampling.}
  \label{fig:flowchart}
\end{figure}

@@

\begin{thebibliography}{10}

\bibitem{bohr2000microwave}
Henrik Bohr and Jakob Bohr.
\newblock Microwave-enhanced folding and denaturation of globular proteins.
\newblock {\em Phys. Rev. E}, 61(4):4310, 2000.

\bibitem{bohr2000microwave-1}
Henrik Bohr and Jakob Bohr.
\newblock Microwave enhanced kinetics observed in ord studies of a protein.
\newblock {\em Bioelectromagnetics}, 21(1):68--72, 2000.

\bibitem{dePomerai2000cell}
David de~Pomerai, Clare Daniells, Helen David, Joanna Allan, Ian Duce, Mohammed
  Mutwakil, David Thomas, Phillip Sewell, John Tattersall, Don Jones, and Peter
  Candido.
\newblock Cell biology: Non-thermal heat-shock response to microwaves.
\newblock {\em Nature}, 405:417--418, 2000.

\bibitem{dePomerai2003microwave}
David~I de~Pomerai, Brette Smith, Adam Dawe, Kate North, Tim Smith, David~B
  Archer, Ian~R Duce, Donald Jones, and E~Peter~M Candido.
\newblock Microwave radiation can alter protein conformation without bulk
  heating.
\newblock {\em FEBS letters}, 543(1):93--97, 2003.

\bibitem{mancinelli2004non}
Fabrizio Mancinelli, Michele Caraglia, Alberto Abbruzzese, Guglielmo
  d'Ambrosio, Rita Massa, and Ettore Bismuto.
\newblock Non-thermal effects of electromagnetic fields at mobile phone
  frequency on the refolding of an intracellular protein: Myoglobin.
\newblock {\em J. Cell. Biochem.}, 93(1):188--196, 2004.

\bibitem{inskip2001cellular}
Peter~D Inskip, Robert~E Tarone, Elizabeth~E Hatch, Timothy~C Wilcosky,
  William~R Shapiro, Robert~G Selker, Howard~A Fine, Peter~M Black, Jay~S
  Loeffler, and Martha~S Linet.
\newblock Cellular-telephone use and brain tumors.
\newblock {\em N. Engl. J. Med.}, 344(2):79--86, 2001.

\bibitem{bekard2013electric}
I.~Bekard and D.E. Dunstan.
\newblock Electric field induced changes in protein conformation.
\newblock {\em Soft Matter}, pages~--, 2014.

\bibitem{budi2005electric}
A.~Budi, F.S. Legge, H.~Treutlein, and I.~Yarovsky.
\newblock Electric field effects on insulin chain-b conformation.
\newblock {\em J. Phys. Chem. B}, 109(47):22641--22648, 2005.

\bibitem{budi2007effect}
A.~Budi, F.S. Legge, H.~Treutlein, and I.~Yarovsky.
\newblock Effect of frequency on insulin response to electric field stress.
\newblock {\em J. Phys. Chem. B}, 111(20):5748--5756, 2007.

\bibitem{budi2008comparative}
Akin Budi, F~Sue Legge, Herbert Treutlein, and Irene Yarovsky.
\newblock Comparative study of insulin chain-b in isolated and monomeric
  environments under external stress.
\newblock {\em J. Phys. Chem. B}, 112(26):7916--7924, 2008.

\bibitem{astrakas2012structural}
Loukas~G Astrakas, Christos Gousias, and Margaret Tzaphlidou.
\newblock Structural destabilization of chignolin under the influence of
  oscillating electric fields.
\newblock {\em J. Appl. Phys.}, 111(7):074702--074702, 2012.

\bibitem{damm2012can}
Markus Damm, Christoph Nusshold, David Cantillo, Gerald~N Rechberger, Karl
  Gruber, Wolfgang Sattler, and C~Oliver Kappe.
\newblock Can electromagnetic fields influence the structure and enzymatic
  digest of proteins? a critical evaluation of microwave-assisted proteomics
  protocols.
\newblock {\em J. Proteomics}, 75:5533--5543, 2012.

\bibitem{english2009nonequilibrium}
N.J. English, G.Y. Solomentsev, and P.~O'Brien.
\newblock Nonequilibrium molecular dynamics study of electric and low-frequency
  microwave fields on hen egg white lysozyme.
\newblock {\em J. Chem. Phys.}, 131:035106, 2009.

\bibitem{solomentsev2012effects}
G.Y. Solomentsev, N.J. English, and D.A. Mooney.
\newblock Effects of external electromagnetic fields on the conformational
  sampling of a short alanine peptide.
\newblock {\em J. Comput. Chem.}, 33:917--923, 2012.

\bibitem{wang2014exploring}
Han Wang, Christof Sch{\"u}tte, Giovanni Ciccotti, and Luigi Delle~Site.
\newblock Exploring the conformational dynamics of alanine dipeptide in
  solution subjected to an external electric field: {A} nonequilibrium
  molecular dynamics simulation.
\newblock {\em Journal of Chemical Theory and Computation}, 10(4):1376--1386,
  2014.

\bibitem{A19-31}
Ch. Sch\"utte and M.~Sarich.
\newblock {\em Metastability and {{Markov}} State Models in Molecular Dynamics:
  Modeling, Analysis, Algorithmic Approaches}, volume~24 of {\em Courant
  Lecture Notes}.
\newblock American Mathematical Society, December 2013.

\bibitem{prinz2011markov}
J.H. Prinz, H.~Wu, M.~Sarich, B.~Keller, M.~Senne, M.~Held, J.D. Chodera,
  C.~Sch{\"u}tte, and F.~No{\'e}.
\newblock {{Markov} models of molecular kinetics: Generation and validation}.
\newblock {\em J. Chem. Phys.}, 134:174105, 2011.

\bibitem{A19-1}
G.~R. Bowman, V.~S. Pande, and F.~No\'e, editors.
\newblock {\em An Introduction to {{Markov}} State Models and Their Application
  to Long Timescale Molecular Simulation}, volume 797 of {\em Advances in
  Experimental Medicine and Biology}.
\newblock Springer, 2014.

\bibitem{A19-49}
M.~Senne, B.~Trendelkamp-Schroer, A.~S. J.~S. Mey, Ch. Sch\"utte, and F.~No\'e.
\newblock Emma - a software package for {{Markov}} model building and analysis.
\newblock {\em J. Chem. Theory Comput.}, 8:2223--2238, 2012.

\bibitem{MSMBuilder}
Kyle~A Beauchamp, Gregory R~Bowman andThomas J~Lane, Lutz Maibaum, Imran~S
  Haque, and Vijay~S Pande.
\newblock {MSMBuilder2}: {M}odeling conformational dynamics at the picosecond
  to millisecond scale.
\newblock {\em J Chem Theor Comput}, 2011.

\bibitem{schuette2011markov}
C.~Sch{\"u}tte, F.~No{\'e}, J.~Lu, M.~Sarich, and E.~Vanden-Eijnden.
\newblock {{Markov} State Models based on Milestoning}.
\newblock {\em J. Chem. Phys.}, 134:204105, 2011.

\bibitem{sarich2010approximation}
Marco Sarich, Frank No{\'e}, and Christof Sch{\"u}tte.
\newblock On the approximation quality of {Markov} state models.
\newblock {\em Multiscale Modeling \& Simulation}, 8(4):1154--1177, 2010.

\bibitem{Eigenvalues}
N.~Djurdjevac, M.~Sarich, and Ch~Sch{\"u}tte.
\newblock Estimating the eigenvalue error of {M}arkov state models.
\newblock {\em Multiscale Modeling \& Simulation}, 10(1):61--81, 2012.

\bibitem{PNAS09}
F.~No\'{e}, C.~Sch\"utte, E.~Vanden-Eijnden, L.~Reich, and T.~R. Weikl.
\newblock Constructing the full ensemble of folding pathways from short
  off-equilibrium simulations.
\newblock {\em Proc. Natl. Acad. Sci. USA}, 106:19011--19016, 2009.

\bibitem{kohlhoff2014cloud}
Kai~J Kohlhoff, Diwakar Shukla, Morgan Lawrenz, Gregory~R Bowman, David~E
  Konerding, Dan Belov, Russ~B Altman, and Vijay~S Pande.
\newblock Cloud-based simulations on google exacycle reveal ligand modulation
  of gpcr activation pathways.
\newblock {\em Nature chemistry}, 6(1):15--21, 2014.

\bibitem{A19-39}
B.~G. Keller, J.-H. Prinz, and F.~No\'e.
\newblock {{Markov}} models and dynamical fingerprints: {U}nraveling the
  complexity of molecular kinetics.
\newblock {\em Chem. Phys.}, 396:92--107, 2012.

\bibitem{PrinzKellerNoe_PCCP11_Perspective}
Jan-Hendrik Prinz, Bettina~G. Keller, and Frank No{\'e}.
\newblock Probing molecular kinetics with {{{Markov}}} models: Metastable
  states, transition pathways and spectroscopic observables.
\newblock {\em Phys. Chem. Chem. Phys.}, 13:16912--16927, 2011.

\bibitem{pande2010everything}
V.S. Pande, K.~Beauchamp, and G.R. Bowman.
\newblock Everything you wanted to know about {Markov} state models but were
  afraid to ask.
\newblock {\em Methods}, 52(1):99--105, 2010.

\bibitem{A19-29}
M.~Sarich, Ralf Banisch, C.~Hartmann, and Ch. Sch\"utte.
\newblock {{Markov}} state models for rare events in molecular dynamics.
\newblock {\em Entropy (Special Issue)}, 16(1):258--286, December 2013.

\bibitem{latorre2011structure}
Juan~C Latorre, Philipp Metzner, Carsten Hartmann, and Christof Sch{\"u}tte.
\newblock A structure-preserving numerical discretization of reversible
  diffusions.
\newblock {\em Commun. Math. Sci}, 9(4):1051--1072, 2011.

\bibitem{floquet1883equations}
G~Floquet.
\newblock Sur les {\'e}quations diff{\'e}rentielles lin{\'e}aires {\`a}
  coefficients p{\'e}riodiques.
\newblock {\em Annales scientifiques de l'{\'E}cole Normale Sup{\'e}rieure},
  12:47--82, 1883.

\bibitem{A19-26}
F.~No\'e, H.~Wu, J.-H. Prinz, and N.~Plattner.
\newblock Projected and hidden {{Markov}} models for calculating kinetics and
  metastable states of complex molecules.
\newblock {\em J. Chem. Phys.}, 139:184114, 2013.

\bibitem{BucheteHummer}
Nicaolae~V. Buchete and Gerhard Hummer.
\newblock Coarse master equations for peptide folding dynamics.
\newblock {\em J. Phys. Chem. B}, 112:6057--6069, 2008.

\bibitem{sarich2014utilizing}
Marco Sarich and Christof Sch{\"u}tte.
\newblock Utilizing hitting times for finding metastable sets in non-reversible
  {Markov} chains.
\newblock {\em submitted to the Journal of Computational Dynamics}, 2014.

\bibitem{discreteTPT}
P.~Metzner, Ch. Sch{\"u}tte, and E.~Vanden-Eijnden.
\newblock Transition path theory for {M}arkov jump processes.
\newblock {\em Multiscale Modeling and Simulation}, 7(3):1192--1219, 2009.

\bibitem{djurdjevac2010markov}
N.~Djurdjevac, M.~Sarich, and C.~Sch{\"u}tte.
\newblock On {{Markov}} state models for metastable processes.
\newblock In {\em Proceedings of the International Congress of Mathematicians},
  volume 901, pages 3105--3131, 2010.

\bibitem{chodera2007automatic}
J.D. Chodera, N.~Singhal, V.S. Pande, K.A. Dill, and W.C. Swope.
\newblock Automatic discovery of metastable states for the construction of
  {Markov} models of macromolecular conformational dynamics.
\newblock {\em J. Chem. Phys.}, 126:155101, 2007.

\bibitem{foloppe2000all}
Nicolas Foloppe and Alexander~D MacKerell~Jr.
\newblock All-atom empirical force field for nucleic acids: I. parameter
  optimization based on small molecule and condensed phase macromolecular
  target data.
\newblock {\em J. Comput. Chem.}, 21(2):86--104, 2000.

\bibitem{jorgensen1983comparison}
William~L Jorgensen, Jayaraman Chandrasekhar, Jeffry~D Madura, Roger~W Impey,
  and Michael~L Klein.
\newblock Comparison of simple potential functions for simulating liquid water.
\newblock {\em J. Chem. Phys.}, 79(2):926--935, 1983.

\bibitem{mackerell2004extending}
Alexander~D MacKerell, Michael Feig, and Charles~L Brooks~III.
\newblock Extending the treatment of backbone energetics in protein force
  fields: Limitations of gas-phase quantum mechanics in reproducing protein
  conformational distributions in molecular dynamics simulations.
\newblock {\em J. Comput. Chem.}, 25(11):1400--1415, 2004.

\bibitem{pronk2013gromacs}
S.~Pronk, S.~P{\'a}ll, R.~Schulz, P.~Larsson, P.~Bjelkmar, R.~Apostolov, M.R.
  Shirts, J.C. Smith, P.M. Kasson, D.~van~der Spoel, Hess B., and Lindahl E.
\newblock Gromacs 4.5: a high-throughput and highly parallel open source
  molecular simulation toolkit.
\newblock {\em Bioinformatics}, pages 1--10, 2013.

\bibitem{bjelkmar2010implementation}
P\"{a}r Bjelkmar, Per Larsson, Michel~A Cuendet, Berk Hess, and Erik Lindahl.
\newblock Implementation of the charmm force field in gromacs: Analysis of
  protein stability effects from correction maps, virtual interaction sites,
  and water models.
\newblock {\em J. Chem. Theory Comput.}, 6(2):459--466, 2010.

\bibitem{parrinello1981polymorphic}
M.~Parrinello and A.~Rahman.
\newblock Polymorphic transitions in single crystals: A new molecular dynamics
  method.
\newblock {\em J. Appl. Phys.}, 52:7182, 1981.

\bibitem{darden1993pme}
T.~Darden, D.~York, and L.~Pedersen.
\newblock {Particle mesh Ewald: An $N \log (N)$ method for Ewald sums in large
  systems}.
\newblock {\em J. Chem. Phys.}, 98:10089, 1993.

\bibitem{essmann1995spm}
U.~Essmann, L.~Perera, M.L. Berkowitz, T.~Darden, H.~Lee, and L.G. Pedersen.
\newblock {A smooth Particle Mesh Ewald method}.
\newblock {\em J. Chem. Phys.}, 103(19):8577, 1995.

\bibitem{wang2010optimizing}
Han Wang, Florian Dommert, and Christian Holm.
\newblock Optimizing working parameters of the smooth particle mesh ewald
  algorithm in terms of accuracy and efficiency.
\newblock {\em The Journal of chemical physics}, 133(3):034117, 2010.

\bibitem{hess1997lincs}
B.~Hess, H.~Bekker, H.J.C. Berendsen, and J.G.E.M. Fraaije.
\newblock {LINCS: a linear constraint solver for molecular simulations}.
\newblock {\em J. Comput. Chem.}, 18(12):1463--1472, 1997.
